Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
got rid of \blindtext lorem ipsumgist

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surface Density of VH$z$Qs}
One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
so, how many are still to be discovered and confirmed spectroscopically?

In the North, we assume the UHS J-band depth of 19.6 \citep[Vega;
][]{Dye2018}.  In the South, one can use the report {\tt ABmagLimits}
for each survey in the database, we can calculate the depths of the
various NIR VISTA surveys.  Fig.~\ref{fig:VHS_J_abMagLim} shows this
calculated average {\tt AB MAGLIM} in the VHS.  As one can see, the
VHS is not completely uniform. The area wrapping round
310$\lesssim$RA/deg$\lesssim$90 and -70$\lesssim$ Decl./ deg
$\lesssim$ -40 has a $J$-band depth of 21.2 AB mag, whereas the rest
of the VHS area, the $J$-band depth is closer to 20.6 AB mag.

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_J_abMagLim.png}
  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
    Y and H are almost uniform, but the coverage is much less.}
  \label{fig:VHS_J_abMagLim}
\end{figure}

Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
exponential decline to describe the space density of VH$z$Qs at high
redshifts, e.g.
\begin{equation}
\rho(z, {\rm M}_{1450}) \propto 10^{k (z)}
\end{equation}
where $z$ is the sample redshift. 
%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, compiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

%%
We can gain a good appreciation for what these missions will discover
by collating the datasets we currently have.

\begin{itemize}
    \item Lorem ipsum dolor sit amet, consectetur adipiscing
      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
      convallis ac. 
    \item Fusce pellentesque condimentum dolor, quis vehicula
      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
      diam eu blandit. Donec in lacinia libero.
    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
      euismod. Cras vel auctor neque. Nam quis diam risus.
\end{itemize}
Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
eu elit massa. Nulla vel lacus lorem. Proin et lobortis
tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
eget tempor elementum, lectus urna feugiat nisi, eget sagittis.

>>>>

We note that sometimes the average flux is negative and so a default
magnitude is reported.  This is apparent for the average $H$ and
$K_{s}$ flux for CFHQS J0216-0455 at MJD=56900.  Interestingly this is
evident in both the $H$ and $K_{s}$ filters, but with this quasar not
much brighter than the detection limit, one must be very careful with
any (over) interpretation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusions}
In this study, we have, for the first time, compiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

\begin{itemize}
    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
    \item The 14 objects that are not detected in the NIR is due to lack of coverage rather than lack of depth; 
   \item 362 ( 78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
 \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
\end{itemize}

The science reach of $z>5$ quasars will continue to be important well into the next decade
\citep{Fan2019_DecadalWP, Wang2019_DecadalWP}
and will provide key insights into direct collapse black holes, hydrogen reionization and
the physics of accretion in the first $\lesssim$700 million years of the Universe.
